\mytitile\\~

### 2019-10-10 document.tex
LF format
Added the sample design picture

@@

A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity. Therefore, in the main text we avoid using the standard charge and phase operators (this approach is covered Appendix) and write down its Hamiltonian using the annihilation operator $\hat b$:
\begin{equation}
\hat H_{tr}/\hbar = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
\end{equation}
where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon. Additionally, by applying external magnetic flux $\Phi_e$ it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}.

@@

\subsection{Master equation solution in QuTiP}

@@

When modelling the experimental behaviour, we

\subsection{Experiment}
\subsubsection{Device design and fabrication}
The chip consist the transmission line capacitively couple to $\lambda/4$ coplanar waveguide resonator which capacitively couple to two transmons. Qubit control is achieved by external microwave driving line and two flux bias lines. 
\subsubsection{Experimental parameters}
\subsubsection{Experimental setup}
The sample was measured in laboratory of artificial quantum systems at Moscow Institute of Physics and Technology. Cryogenic equipment was
represented by BlueFors LD250 dilution refrigerator, with base temperature of 16 mK. The microwave equipment included KEYSIGHT PNA-L N5232A 300 kHz-20 GHz vector network analyser, Agilent MXG N5183B 9 kHz - 40 GHz analog signal generator. The sample was 
flux biased using YOKOGAWA GS200 current source.

>>>>

\subsection{Experiment}
\subsubsection{Device design and fabrication}
The chip consist the transmission line capacitively couple to $\lambda/4$ coplanar waveguide resonator which capacitively couple to two transmons. Qubit control is achieved by external microwave driving line and two flux bias lines.

\begin{figure}
	\includegraphics[width=\linewidth]{experiment}
	\caption{Experimental details. \textbf{(a)} Sample optical photograph \textbf{(b)} Electrical scheme \textbf{(c)} Spectral lines of the qubits}
\end{figure}

\subsubsection{Experimental parameters}
\subsubsection{Experimental setup}
The sample was measured in laboratory of artificial quantum systems at Moscow Institute of Physics and Technology. Cryogenic equipment was
represented by BlueFors LD250 dilution refrigerator, with base temperature of 16 mK. The microwave equipment included KEYSIGHT PNA-L N5232A 300 kHz-20 GHz vector network analyser, Agilent MXG N5183B 9 kHz - 40 GHz analog signal generator. The sample was 
flux biased using YOKOGAWA GS200 current source.

@@

A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity. Therefore, in the main text we avoid using the standard charge and phase operators (this approach is covered Appendix) and write down its Hamiltonian using the annihilation operator $\hat b$:
\begin{equation}
\hat H_{tr}/\hbar = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
\end{equation}
where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or the  $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon. Additionally, by applying external magnetic flux $\Phi_e$ it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}.

@@

\subsection{Master equation solution in \textit{qutip}}

@@

Two distinct modes of operation were used during the
